Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-11-27 Moltres.tex
backed up claims on MSRs being good on fuel

Molten salt reactor concepts garnered considerable interest in the 1950s and 60s
with development of the \gls{ARE} and later the \gls{MSRE} at \gls{ORNL}.  With
the inclusion of the \gls{MSR} among the Generation-IV reactor designs
\cite{gif_generation_2008,gif_generation_2015}, this reactor concept has gained
renewed research interest in the past decade, with many new nuclear companies
proposing both fluid-fuelled and solid-fuelled commercial \gls{MSR} designs
\cite{hyde_liquid_2015,leblanc_integral_2015,thorcon_-able_2017,scarlat_design_2014,transatomic_power_corporation_neutronics_2016}.
Two key advantages offered by the fluid-fuelled \gls{MSR} are improved fuel
utilization and no radiation damage constraint on attainable fuel
burn-up. Together these attributes can result in significantly reduced spent
fuel mass and, in the case of fluoride salt reactors in particular, reduced core
fissile inventories \cite{gif_generation_2008,gif_generation_2015}.  Due to
these characteristics, the \gls{MSR} is potentially uniquely capable of burning
actinides and extending fuel resources.

@@

Parallelization in Moltres is implemented via LibMesh, which includes a set of
utilities for massively parallel finite element based computations, including
mesh input/output, a finite element library, and an interface for connections with
solver packages. Employing LibMesh provides Moltres with
significant flexibility including the ability to swap out solver libraries
such as PetSc, which includes an expanding suite of parallel linear and
nonlinear solvers. Problem domain decomposition relies on LibMesh mesh
adaptation capabilities for running on a specific number of processors and
can either be performed manually before the start of the simulation or
automatically at the parameters of computation.

>>>>

Molten salt reactor concepts garnered considerable interest in the 1950s and 60s
with development of the \gls{ARE} and later the \gls{MSRE} at \gls{ORNL}.  With
the inclusion of the \gls{MSR} among the Generation-IV reactor designs
\cite{gif_generation_2008,gif_generation_2015}, this reactor concept has gained renewed research
interest in the past decade, with many new nuclear companies proposing both
fluid-fuelled and solid-fuelled commercial \gls{MSR} designs
\cite{hyde_liquid_2015,leblanc_integral_2015,thorcon_-able_2017,scarlat_design_2014,transatomic_power_corporation_neutronics_2016}. 
The key advantages of \gls{MSR}s generally pertain to improved fuel utilization
and reactor safety. In contrast to legacy reactors, only moderator fast neutron
damage and fuel chemistry evolution limit burnup. A clever configuration of moderator
as in \cite{engel_conceptual_1980} can enable reactor operation without opening the vessel
for thirty or more years. Further, several fission products selectively precipitate onto
nickel surfaces in fluoride salt, as documented in \cite{engel_conceptual_1980}, thus reducing
unwanted neutron absorption. Lastly, the epithermal spectrum of graphite-moderated salt reactors
incinerates plutonium more efficiently, thus reducing long-lived transuranic waste production \cite{engel_conceptual_1980}. 
The sum of the aforementioned benefits imply spent nuclear fuel
mass can be reduced in comparison to legacy reactors.
Due to these characteristics, the \gls{MSR} is potentially uniquely capable of 
extending fuel resources and ameliorating spent fuel burden.

@@

Parallelization in Moltres is implemented via LibMesh, which includes a set of
utilities for massively parallel finite element based computations, including
mesh input/output, a finite element library, and an interface for connections with
solver packages. Employing LibMesh provides Moltres
significant flexibility including the ability to swap out solver libraries
such as PetSc, which includes an expanding suite of parallel linear and
nonlinear solvers. Problem domain decomposition relies on LibMesh mesh
adaptation capabilities for running on a specific number of processors and
can either be performed manually before the start of the simulation or
automatically at the parameters of computation.
